Towards Practical First-Order Model Counting

### 2025-06-14 doc/talk/friends.tex
Better plots

% Created by tikzDevice version 0.12.6 on 2025-06-13 10:42:02
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (307.15,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{255,255,255}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,203.77) -- ( 38.84,203.77);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{gray}{0.30}

>>>>

% Created by tikzDevice version 0.12.6 on 2025-06-14 12:06:26
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (307.15,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{gray}{0.92}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,203.77) -- ( 38.84,203.77);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
	(229.15,201.57) --
	(244.79,192.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
	(290.40,201.57) --
	(274.75,210.61);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
	(268.15,194.45) --
	(268.07,194.45) --
	(268.39,194.46) --
	(268.71,194.53) --
	(269.01,194.64) --
	(269.29,194.80) --
	(269.53,195.00) --
	(269.75,195.24) --
	(269.92,195.51) --
	(270.04,195.81) --
	(270.12,196.12) --
	(270.15,196.44) --
	(270.15,196.44) --
	(270.15,206.70) --
	(270.15,206.70) --
	(270.12,207.02) --
	(270.04,207.34) --
	(269.92,207.63) --
	(269.75,207.90) --
	(269.53,208.14) --
	(269.29,208.35) --
	(269.01,208.51) --
	(268.71,208.62) --
	(268.39,208.68) --
	(268.15,208.70) --
	(251.39,208.70) --
	(251.63,208.68) --
	(251.31,208.70) --
	(250.99,208.66) --
	(250.68,208.57) --
	(250.39,208.43) --
	(250.12,208.25) --
	(249.89,208.03) --
	(249.70,207.77) --
	(249.55,207.49) --
	(249.45,207.18) --
	(249.40,206.86) --
	(249.39,206.70) --
	(249.39,196.44) --
	(249.40,196.60) --
	(249.40,196.28) --
	(249.45,195.96) --
	(249.55,195.66) --
	(249.70,195.37) --
	(249.89,195.12) --
	(250.12,194.90) --
	(250.39,194.71) --
	(250.68,194.58) --
	(250.99,194.49) --
	(251.31,194.45) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
	(268.15,194.45) --
	(268.07,194.45) --
	(268.39,194.46) --
	(268.71,194.53) --
	(269.01,194.64) --
	(269.29,194.80) --
	(269.53,195.00) --
	(269.75,195.24) --
	(269.92,195.51) --
	(270.04,195.81) --
	(270.12,196.12) --
	(270.15,196.44) --
	(270.15,196.44) --
	(270.15,206.70) --
	(270.15,206.70) --
	(270.12,207.02) --
	(270.04,207.34) --
	(269.92,207.63) --
	(269.75,207.90) --
	(269.53,208.14) --
	(269.29,208.35) --
	(269.01,208.51) --
	(268.71,208.62) --
	(268.39,208.68) --
	(268.15,208.70) --
	(251.39,208.70) --
	(251.63,208.68) --
	(251.31,208.70) --
	(250.99,208.66) --
	(250.68,208.57) --
	(250.39,208.43) --
	(250.12,208.25) --
	(249.89,208.03) --
	(249.70,207.77) --
	(249.55,207.49) --
	(249.45,207.18) --
	(249.40,206.86) --
	(249.39,206.70) --
	(249.39,196.44) --
	(249.40,196.60) --
	(249.40,196.28) --
	(249.45,195.96) --
	(249.55,195.66) --
	(249.70,195.37) --
	(249.89,195.12) --
	(250.12,194.90) --
	(250.39,194.71) --
	(250.68,194.58) --
	(250.99,194.49) --
	(251.31,194.45) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
	(268.15,194.45) --
	(268.07,194.45) --
	(268.39,194.46) --
	(268.71,194.53) --
	(269.01,194.64) --
	(269.29,194.80) --
	(269.53,195.00) --
	(269.75,195.24) --
	(269.92,195.51) --
	(270.04,195.81) --
	(270.12,196.12) --
	(270.15,196.44) --
	(270.15,196.44) --
	(270.15,206.70) --
	(270.15,206.70) --
	(270.12,207.02) --
	(270.04,207.34) --
	(269.92,207.63) --
	(269.75,207.90) --
	(269.53,208.14) --
	(269.29,208.35) --
	(269.01,208.51) --
	(268.71,208.62) --
	(268.39,208.68) --
	(268.15,208.70) --
	(251.39,208.70) --
	(251.63,208.68) --
	(251.31,208.70) --
	(250.99,208.66) --
	(250.68,208.57) --
	(250.39,208.43) --
	(250.12,208.25) --
	(249.89,208.03) --
	(249.70,207.77) --
	(249.55,207.49) --
	(249.45,207.18) --
	(249.40,206.86) --
	(249.39,206.70) --
	(249.39,196.44) --
	(249.40,196.60) --
	(249.40,196.28) --
	(249.45,195.96) --
	(249.55,195.66) --
	(249.70,195.37) --
	(249.89,195.12) --
	(250.12,194.90) --
	(250.39,194.71) --
	(250.68,194.58) --
	(250.99,194.49) --
	(251.31,194.45) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
	(268.15,194.45) --
	(268.07,194.45) --
	(268.39,194.46) --
	(268.71,194.53) --
	(269.01,194.64) --
	(269.29,194.80) --
	(269.53,195.00) --
	(269.75,195.24) --
	(269.92,195.51) --
	(270.04,195.81) --
	(270.12,196.12) --
	(270.15,196.44) --
	(270.15,196.44) --
	(270.15,206.70) --
	(270.15,206.70) --
	(270.12,207.02) --
	(270.04,207.34) --
	(269.92,207.63) --
	(269.75,207.90) --
	(269.53,208.14) --
	(269.29,208.35) --
	(269.01,208.51) --
	(268.71,208.62) --
	(268.39,208.68) --
	(268.15,208.70) --
	(251.39,208.70) --
	(251.63,208.68) --
	(251.31,208.70) --
	(250.99,208.66) --
	(250.68,208.57) --
	(250.39,208.43) --
	(250.12,208.25) --
	(249.89,208.03) --
	(249.70,207.77) --
	(249.55,207.49) --
	(249.45,207.18) --
	(249.40,206.86) --
	(249.39,206.70) --
	(249.39,196.44) --
	(249.40,196.60) --
	(249.40,196.28) --
	(249.45,195.96) --
	(249.55,195.66) --
	(249.70,195.37) --
	(249.89,195.12) --
	(250.12,194.90) --
	(250.39,194.71) --
	(250.68,194.58) --
	(250.99,194.49) --
	(251.31,194.45) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
	(268.15,194.45) --
	(268.07,194.45) --
	(268.39,194.46) --
	(268.71,194.53) --
	(269.01,194.64) --
	(269.29,194.80) --
	(269.53,195.00) --
	(269.75,195.24) --
	(269.92,195.51) --
	(270.04,195.81) --
	(270.12,196.12) --
	(270.15,196.44) --
	(270.15,196.44) --
	(270.15,206.70) --
	(270.15,206.70) --
	(270.12,207.02) --
	(270.04,207.34) --
	(269.92,207.63) --
	(269.75,207.90) --
	(269.53,208.14) --
	(269.29,208.35) --
	(269.01,208.51) --
	(268.71,208.62) --
	(268.39,208.68) --
	(268.15,208.70) --
	(251.39,208.70) --
	(251.63,208.68) --
	(251.31,208.70) --
	(250.99,208.66) --
	(250.68,208.57) --
	(250.39,208.43) --
	(250.12,208.25) --
	(249.89,208.03) --
	(249.70,207.77) --
	(249.55,207.49) --
	(249.45,207.18) --
	(249.40,206.86) --
	(249.39,206.70) --
	(249.39,196.44) --
	(249.40,196.60) --
	(249.40,196.28) --
	(249.45,195.96) --
	(249.55,195.66) --
	(249.70,195.37) --
	(249.89,195.12) --
	(250.12,194.90) --
	(250.39,194.71) --
	(250.68,194.58) --
	(250.99,194.49) --
	(251.31,194.45) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
	(268.15,194.45) --
	(268.07,194.45) --
	(268.39,194.46) --
	(268.71,194.53) --
	(269.01,194.64) --
	(269.29,194.80) --
	(269.53,195.00) --
	(269.75,195.24) --
	(269.92,195.51) --
	(270.04,195.81) --
	(270.12,196.12) --
	(270.15,196.44) --
	(270.15,196.44) --
	(270.15,206.70) --
	(270.15,206.70) --
	(270.12,207.02) --
	(270.04,207.34) --
	(269.92,207.63) --
	(269.75,207.90) --
	(269.53,208.14) --
	(269.29,208.35) --
	(269.01,208.51) --
	(268.71,208.62) --
	(268.39,208.68) --
	(268.15,208.70) --
	(251.39,208.70) --
	(251.63,208.68) --
	(251.31,208.70) --
	(250.99,208.66) --
	(250.68,208.57) --
	(250.39,208.43) --
	(250.12,208.25) --
	(249.89,208.03) --
	(249.70,207.77) --
	(249.55,207.49) --
	(249.45,207.18) --
	(249.40,206.86) --
	(249.39,206.70) --
	(249.39,196.44) --
	(249.40,196.60) --
	(249.40,196.28) --
	(249.45,195.96) --
	(249.55,195.66) --
	(249.70,195.37) --
	(249.89,195.12) --
	(250.12,194.90) --
	(250.39,194.71) --
	(250.68,194.58) --
	(250.99,194.49) --
	(251.31,194.45) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
	(268.15,194.45) --
	(268.07,194.45) --
	(268.39,194.46) --
	(268.71,194.53) --
	(269.01,194.64) --
	(269.29,194.80) --
	(269.53,195.00) --
	(269.75,195.24) --
	(269.92,195.51) --
	(270.04,195.81) --
	(270.12,196.12) --
	(270.15,196.44) --
	(270.15,196.44) --
	(270.15,206.70) --
	(270.15,206.70) --
	(270.12,207.02) --
	(270.04,207.34) --
	(269.92,207.63) --
	(269.75,207.90) --
	(269.53,208.14) --
	(269.29,208.35) --
	(269.01,208.51) --
	(268.71,208.62) --
	(268.39,208.68) --
	(268.15,208.70) --
	(251.39,208.70) --
	(251.63,208.68) --
	(251.31,208.70) --
	(250.99,208.66) --
	(250.68,208.57) --
	(250.39,208.43) --
	(250.12,208.25) --
	(249.89,208.03) --
	(249.70,207.77) --
	(249.55,207.49) --
	(249.45,207.18) --
	(249.40,206.86) --
	(249.39,206.70) --
	(249.39,196.44) --
	(249.40,196.60) --
	(249.40,196.28) --
	(249.45,195.96) --
	(249.55,195.66) --
	(249.70,195.37) --
	(249.89,195.12) --
	(250.12,194.90) --
	(250.39,194.71) --
	(250.68,194.58) --
	(250.99,194.49) --
	(251.31,194.45) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
